---
title: "Assignment 1"
---

# Assignment 1

My first assignment has four parts.

## (a)

I have watched this [**video**](https://www.youtube.com/watch?v=t8qtcDyCRFA&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=13). In this video, a man shows that how to create a blog from scratch and publish it into the web on Quarto Pub using Quarto.

## (b)

-   First difference I want to talk about is data structures. While lists, dictionaries, tuples are more primary in Python, vectors, matrices and dataframes are at the primary in R.

-   Second difference is indexing. In Python indexing starts with 0 but in R indexing starts with 1.

    ```{python}
    vector = [0,1,2]
    vector[0]
    ```

    ```{r}
    vector_ <- c(0,1,2)
    vector_[1]
    ```

-   Third difference is assignment operator. In R, we can use "\<-" but in Python we have to use "="

```{r}
a <- 10
a
```

```{python}
a = 10
a
```

## (c)

```{r}
library(dslabs)


data <- na_example
data

sum(is.na(data))

```

```{r}
data_0 <- data
data_0[is.na(data)] <- 0
data_0
sum(is.na(data_0))
```
